---
title: "sample_analysis_grplasso_survrrr"
output: pdf_document
date: "2026-02-06"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# source needed packages and files
```{r}
library(Rcpp)
library(RcppEigen)
library(mstate)

sourceCpp("src/grplasso_survrrr.cpp")
source("grplasso_survrrr.R")
sourceCpp("src/lasso_survrrr.cpp")
source("lasso_survrrr.R")
source("survRRR_functions.R")
source("simdata_function_and_performance_functions.R")
```

# unpenalized model

```{r}
set.seed(20020607)
n <- 1000
p <- 10
r <- 2
k <- 6
```

```{r}
sim_data1 <- simulations_data(n, p, r, k, case = 1, n_simulations = 200, store_dlong = TRUE)
```

```{r}
rank_check(sim_data1$Beta_matrix)
```

```{r}
perf_grplasso_1  <- simulations_fit_and_performance(sim_data1, p, k, n_simulations = 200, r, lambda_alpha = 0, group_labels = rep(1L, 10), method = "rrr_grplasso")
```

```{r}
perf_lasso_1 <- simulations_fit_and_performance(sim_data1, p, k, n_simulations = 200, r, lambda_alpha = 0, method = "rrr_lasso")
```

```{r}
perf_pen_1 <- simulations_fit_and_performance(sim_data1, 100, k, 10, r, lambda_alpha = 0, method = "pen")
```

```{r}
comparison <- data.frame(
  method   = c("rrr_grplasso", "rrr_lasso", "pen"),
  mean_bias = c(mean(perf_grplasso_1$bias1), mean(perf_lasso_1$bias1), mean(perf_pen_1$bias1)),
  mean_mse  = c(mean(perf_grplasso_1$mse1),  mean(perf_lasso_1$mse1),  mean(perf_pen_1$mse1)),
  mean_corr = c(mean(perf_grplasso_1$cor_coeff_vec), mean(perf_lasso_1$cor_coeff_vec), mean(perf_pen_1$cor_coeff_vec))
)
print(comparison)
```

# penalized model (case 2)
# 4 groups
```{r}
set.seed(20020607)
n <- 3000
p <- 30
r <- 2
k <- 12
n_groups <- 3
zero_blocks <- list(c(1, 1), c(3, 2), c(2, 1)) # group1 rank1; group3 rank2
```

## search the best lambda

```{r}
search_data <- simulations_data(n, p, r, k, n_simulations = 10, n_groups=n_groups, zero_blocks=zero_blocks, store_dlong = TRUE, case = 2, group_corr = 0.7)

group_labels <- search_data$group_labels
pred_names <- paste0("x", 1:p)
```

```{r}
lambda_vector <- seq(1e-8,1e-2,length.out=4)
lambda_grp_lasso_1 <- simulations_fit_find_best_lambda(search_data, lambda_vector, p, k, r, group_labels, method = "rrr_grplasso", n_folds_0 = 5)

best_lam_grp_1 <- lambda_grp_lasso_1$best_lambda
```

```{r}
lambda_vector <- seq(1e-8,1e-2,length.out=4)
lambda_lasso_1  <- simulations_fit_find_best_lambda(search_data, lambda_vector, p, k, r, method = "rrr_lasso", n_folds_0 = 5)
```

```{r}
lambda_vector <- seq(1e-18,1e-8,length.out=5)
lambda_pen_1  <- simulations_fit_find_best_lambda(search_data, lambda_vector, p, k, r, method = "pen")
```

```{r}
sim_data2 <- simulations_data(n, p, r, k, n_simulations = 10, store_dlong = TRUE,group_corr = 0.7)
```

```{r}
rank_check(sim_data2$Beta_matrix)
```

```{r}
perf_grplasso_2  <- simulations_fit_and_performance(sim_data2, p, k, n_simulations = 10, r, lambda_alpha = 0.001, group_labels, method = "rrr_grplasso")
```

```{r}
perf_lasso_2 <- simulations_fit_and_performance(sim_data2, p, k, 10, r, lambda_alpha = 0.001, method = "rrr_lasso")
```

```{r}
perf_pen_2  <- simulations_fit_and_performance(sim_data2, p, k, 10, r,
               lambda_alpha = 1e-8, method = "pen")
```

```{r}
comparison2 <- data.frame(
  method   = c("rrr_grplasso", "rrr_lasso", "pen"),
  mean_bias = c(mean(perf_grplasso_2$bias1), mean(perf_lasso_2$bias1), mean(perf_pen_2$bias1)),
  mean_mse  = c(mean(perf_grplasso_2$mse1),  mean(perf_lasso_2$mse1), mean(perf_pen_2$mse1)),
  mean_corr = c(mean(perf_grplasso_2$cor_coeff_vec), mean(perf_lasso_2$cor_coeff_vec), mean(perf_pen_2$cor_coeff_vec))
)
print(comparison2)
```


## lasso + gradient descent

```{r}
sim_data_l_1 <- simulations_data(n, p, r, k,
                                n_simulations = n_simulations,
                                case = 1)

perf_l_1 <- simulations_fit_and_performance(
  datas = sim_data_grpl_1,
  p = p,
  k = k,
  n_simulations = n_simulations,
  r = r,
  lambda_alpha = 0,
  group_labels = rep(1L, p),
  lambda_idx   = 1
  )
```

# fit models

## group lasso + gradient descent
```{r}
group_labels <- rep(1:4, each = 3) # every 3 predictors form a group -> 4 groups
lambda_seq <- seq(0,0.1,by=0.01)
fit_grplasso <- solve_reduced_rank(
  X            = X,
  y_list       = y_list,
  status_list  = status_list,
  R            = 2,
  group_labels = group_labels,
  lambda_alpha = lambda_seq,
  rho          = 0.01, # penalizaed factor for ridge
  step_size    = 0.5,
  max_iter     = 500,
  verbose      = TRUE,
  tol = 1e-6
)
```

## lasso + gradient descent
```{r}
lambda_seq <- seq(0,0.01,by=0.001)
fit_lasso <- solve_reduced_rank_lasso(
  X            = X,
  y_list       = y_list,
  status_list  = status_list,
  R            = 2,
  lambda_alpha = lambda_seq,
  rho          = 0.01, # penalizaed factor for ridge
  step_size    = 0.5,
  max_iter     = 500,
  verbose      = TRUE,
  tol = 1e-6
)
```

## lasso + criss-cross
```{r}
data <- data.frame(id = 1:n)

for(i in 1:K) {
  data[[paste0("t", i)]] <- y_list[[i]]
  data[[paste0("d", i)]] <- status_list[[i]]
}
for (i in 1:p) {
  data[[paste0("x", i)]] <- X[, i]
}
```

```{r}
# Transition matrix(K outcomes) 
tmat <- trans.comprisk(K)

# Column names for survival times and event indicators (can be different depending on dataset that is used!)
tnames <- paste("t", 1:K, sep="")
dnames <- paste("d", 1:K, sep="")

# Create dlong
dlong <- data.frame(
  id = rep(data$id, each = K),
  Tstart = 0,
  Tstop = c(t(matrix(unlist(c(data[, tnames])), n, K))),
  status = c(t(matrix(unlist(c(data[, dnames])), n, K))),
  from = 1,
  to = rep(2:(K+1), n),
  trans = rep(1:K, n)
)

#add predictors (can be different depending on dataset that is used!)
predictor_names <- grep("^x", names(data), value = TRUE)
# Add each predictor to the dlong data frame
for (predictor in predictor_names) {
  dlong[[predictor]] <- rep(data[[predictor]], each = K)
}

# Calculate the time
dlong$time <- dlong$Tstop - dlong$Tstart

# Define the transition matrix and class 
class(dlong) <- c("msdata", "data.frame")
attr(dlong, "trans") <- tmat
```

```{r}
predictor_names <- grep("^x", names(dlong), value = TRUE)
formula_str <- paste("Surv(Tstop, status) ~", paste(predictor_names, collapse = " + "))
formula <- as.formula(formula_str)
```

```{r}
fit_lasso_2 <- pen.survrrr(formula, dat = dlong, R = 2,Gamma.iter = t(Gamma_true), 
          eps = 1e-4, 
          lambda.alpha = 0.005, 
          lambda.gamma = 0.005,  
          standardize.opt = F,
          alpha = 1)
```

# compare B (identifiable)
## group lasso + gradient descent
```{r}
B_hat_grplasso <- fit_grplasso[["result"]][[2]][["B"]]
B_frob_grplasso <- norm(B_hat_grplasso - B_true, "F")
B_rel_grplasso <- B_frob_grplasso/ norm(B_true, "F")
B_frob_grplasso # ||B_hat - B_true||_F
B_rel_grplasso # Relative error
```

```{r}
per_outcome_grplasso <- data.frame(
      outcome = paste0("k=", 1:K),
      cor     = NA_real_,
      mse     = NA_real_,
      bias    = NA_real_,
      rel_err = NA_real_
    )
    
for(k in 1:K) {
  b_hat_grplasso_k  <- B_hat_grplasso[, k]
  b_true_k <- B_true[, k]
  diff_k   <- b_hat_grplasso_k - b_true_k
      
  per_outcome_grplasso$cor[k]     <- cor(b_hat_grplasso_k, b_true_k)
  per_outcome_grplasso$mse[k]     <- mean(diff_k^2)
  per_outcome_grplasso$bias[k]    <- mean(diff_k)
  per_outcome_grplasso$rel_err[k] <- sqrt(sum(diff_k^2)) / sqrt(sum(b_true_k^2))
}
per_outcome_grplasso
```

## lasso + gradient descent
```{r}
B_hat_lasso <- fit_lasso[["result"]][[8]][["B"]]
B_frob_lasso <- norm(B_hat_lasso - B_true, "F")
B_rel_lasso <- B_frob_lasso / norm(B_true, "F")
B_frob_lasso # ||B_hat - B_true||_F
B_rel_lasso # Relative error
```

```{r}
per_outcome_lasso <- data.frame(
      outcome = paste0("k=", 1:K),
      cor     = NA_real_,
      mse     = NA_real_,
      bias    = NA_real_,
      rel_err = NA_real_
    )
    
for(k in 1:K) {
  b_hat_lasso_k  <- B_hat_lasso[, k]
  b_true_k <- B_true[, k]
  diff_k   <- b_hat_lasso_k - b_true_k
      
  per_outcome_lasso$cor[k]     <- cor(b_hat_lasso_k, b_true_k)
  per_outcome_lasso$mse[k]     <- mean(diff_k^2)
  per_outcome_lasso$bias[k]    <- mean(diff_k)
  per_outcome_lasso$rel_err[k] <- sqrt(sum(diff_k^2)) / sqrt(sum(b_true_k^2))
}
per_outcome_lasso
```

```{r}
B_hat_lasso_2 <- fit_lasso_2$Alpha %*% fit_lasso_2$Gamma
```

```{r}
B_frob_lasso_2 <- norm(B_hat_lasso_2 - B_true, "F")
B_rel_lasso_2 <- B_frob_lasso_2 / norm(B_true, "F")
B_frob_lasso_2 # ||B_hat - B_true||_F
B_rel_lasso_2 # Relative error
```

```{r}
per_outcome_lasso_2 <- data.frame(
      outcome = paste0("k=", 1:K),
      cor     = NA_real_,
      mse     = NA_real_,
      bias    = NA_real_,
      rel_err = NA_real_
    )
    
for(k in 1:K) {
  b_hat_lasso_2_k  <- B_hat_lasso_2[, k]
  b_true_k <- B_true[, k]
  diff_k   <- b_hat_lasso_2_k - b_true_k
      
  per_outcome_lasso_2$cor[k]     <- cor(b_hat_lasso_2_k, b_true_k)
  per_outcome_lasso_2$mse[k]     <- mean(diff_k^2)
  per_outcome_lasso_2$bias[k]    <- mean(diff_k)
  per_outcome_lasso_2$rel_err[k] <- sqrt(sum(diff_k^2)) / sqrt(sum(b_true_k^2))
}
per_outcome_lasso_2
```

# compare alpha and Gamma
## functions
```{r}
procrustes <- function(A_hat, A_true) {
      sv  <- svd(t(A_hat) %*% A_true)
      Q   <- sv$v %*% t(sv$u)          # find optimal rotation to minimize ||alpha_hat%*%Q - alpha_true||_F
      list(aligned = A_hat %*% Q, Q = Q)
    }
```

```{r}
# compare span(M1) and span(M2)
subspace_dist <- function(M1, M2) {
      Q1 <- qr.Q(qr(M1));  Q2 <- qr.Q(qr(M2)) # Orthonormal basis of span(M1)/span(M2)
      sv <- pmin(svd(t(Q1) %*% Q2)$d, 1) # cosines of the principal angles between subspaces
      list(angles_degree = acos(sv) * 180 / pi, # to degrees
           subspace_distance  = sqrt(1 - min(sv)^2)) # subspace distance defined via the largest principal angle
    }
```

```{r}
# Varimax
library(GPArotation)
post_process <- function(alpha, Gamma) {
  rot   <- varimax(alpha)
  Q     <- rot$rotmat # Varimax finds an orthogonal rotation Q that maximizes the sparsity (simple structure) of the loadings
  alpha_rot <- alpha %*% Q
  Gamma_rot <- Gamma %*% Q
  
  # for each factor, ensure that the entry of alpha with the largest absolute magnitude is positive
  for(r in 1:ncol(alpha_rot)) {
    if(alpha_rot[which.max(abs(alpha_rot[,r])), r] < 0) {
      alpha_rot[,r] <- -alpha_rot[,r]
      Gamma_rot[,r] <- -Gamma_rot[,r]
    }
  }

  ord <- order(sqrt(colSums(alpha_rot^2)), decreasing = TRUE) # factors with larger overall loading magnitude are placed first
  list(alpha = alpha_rot[, ord], Gamma = Gamma_rot[, ord]) # return rotated and ordered factor matrices
}
```

```{r}
normalize_cols <- function(M) {
  norms <- sqrt(colSums(M^2))
  M %*% diag(1 / norms)
}
```

## group lasso + gradient descent
```{r}
sa_grplasso <- subspace_dist(fit_grplasso[["result"]][[2]][["alpha"]], alpha_true)
sa_grplasso
sg_grplasso <- subspace_dist(fit_grplasso[["result"]][[2]][["Gamma"]], Gamma_true)
sg_grplasso
```

```{r}
pp_grplasso <- post_process(fit_grplasso$result[[2]]$alpha,
                            fit_grplasso$result[[2]]$Gamma)


alpha_pp_norm_grplasso <- normalize_cols(pp_grplasso$alpha)
alpha_true_norm <- normalize_cols(alpha_true)
pa_grplasso <- procrustes(alpha_pp_norm_grplasso, alpha_true_norm)
for(r in 1:2)
  cat(sprintf("Factor %d direction cor after Varimax: %.4f\n", r,
              cor(pa_grplasso$aligned[,r], alpha_true_norm[,r])))
```

```{r}
pp_lasso$alpha
#pp$Gamma
```

## lasso + gradient descent
```{r}
sa_lasso <- subspace_dist(fit_lasso[["result"]][[8]][["alpha"]], alpha_true)
sa_lasso
sg_lasso <- subspace_dist(fit_lasso[["result"]][[8]][["Gamma"]], Gamma_true)
sg_lasso
```

```{r}
pp_lasso <- post_process(fit_lasso$result[[8]]$alpha,
                         fit_lasso$result[[8]]$Gamma)


alpha_pp_norm_lasso <- normalize_cols(pp_lasso$alpha)
pa_lasso <- procrustes(alpha_pp_norm_lasso, alpha_true_norm)
for(r in 1:2)
  cat(sprintf("Factor %d direction cor after Varimax: %.4f\n", r,
              cor(pa_lasso$aligned[,r], alpha_true_norm[,r])))
```

## lasso + criss_cross
```{r}
sa_lasso_2 <- subspace_dist(fit_lasso_2$Alpha, alpha_true)
sa_lasso_2
sg_lasso_2 <- subspace_dist(t(fit_lasso_2$Gamma), Gamma_true)
sg_lasso_2
```
```{r}
pp_lasso_2 <- post_process(fit_lasso_2$Alpha,
                         t(fit_lasso_2$Gamma))


alpha_pp_norm_lasso_2 <- normalize_cols(pp_lasso_2$alpha)
pa_lasso_2 <- procrustes(alpha_pp_norm_lasso_2, alpha_true_norm)
for(r in 1:2)
  cat(sprintf("Factor %d direction cor after Varimax: %.4f\n", r,
              cor(pa_lasso_2$aligned[,r], alpha_true_norm[,r])))
```


