---
title: "sample_analysis_update2"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Source packages and files
```{r}
library(Rcpp)
library(RcppEigen)
library(mstate)
library(tidyr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(scales)
library(patchwork)

sourceCpp("group_lasso_gd/grplasso_survrrr.cpp")
source("group_lasso_gd/grplasso_survrrr.R")
sourceCpp("lasso_gd/lasso_survrrr.cpp")
source("lasso_gd/lasso_survrrr.R")
sourceCpp("ridge_gd/ridge_survrrr.cpp")
source("ridge_gd/ridge_survrrr.R")
sourceCpp("mrcox/aligned.cpp")
source("mrcox/mrcox.R")
source("lasso_cc/survRRR_functions.R")
source("simdata_function_and_performance_functions.R")
```


# Global parameters for case = 2
```{r global-case2-params}
rho_w <- 0.7    # within-group correlation for KMS Toeplitz on alpha
rho_b <- 0.1    # between-group correlation for KMS Toeplitz on alpha
rho_w_k <- 0.7    # within-group correlation for KMS Toeplitz on Gamma
rho_b_k <- 0.1    # between-group correlation for KMS Toeplitz on Gamma
mu_l <- 0.5    # lower bound for group mean (active groups)
mu_u  <- 1.5   # upper bound for group mean (active groups)
use_kms_beta <- TRUE  # use KMS covariance for A_matrix columns
```

# ============================================================
# S0: Low-dimensional, no penalization
# p=20, n=300, case=1
# ============================================================
```{r s0-data}
n <- 300; p <- 20; r_true <- 2; k <- 4

set.seed(7)
sim_data0 <- simulations_data(n, p, r_true, k,
                               case = 1,
                               n_simulations = 100,
                               store_dlong = TRUE)
generate_data_plots(sim_data0$dlong_list[[1]], n = n, r = r_true, p = p, k = k)
```

```{r s0-fit}
# lambda = 0
lv_0 <- 0

set.seed(7)
auto_grplasso_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, group_labels = rep(1L, p),
  method = "rrr_grplasso", rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_lasso_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "rrr_lasso",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_ridge_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "rrr_ridge",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_pen_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "pen",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_mrcox_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "mrcox",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)
```

```{r s0-results}
print_rank_comparisons(
  list(auto_grplasso_0, auto_lasso_0, auto_ridge_0, auto_pen_0, auto_mrcox_0),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S0: n=300, p=20, case=1, lambda=0"
)
```

# ============================================================
# Penalized scenarios — case=2, p=100
#  n (80/300) x n_groups (10/20) x zero_pct (40%/60%)
# pen omitted for n=80 (n < p)
# ============================================================

# ============================================================
# S1: n=80, 10 groups (size=10), 40% zero groups  [n < p]
# ============================================================
```{r s1-setup}
n <- 80; p <- 100; r_true <- 2; k <- 4
n_groups  <- 10
zero_blocks <- c(1, 3, 5, 7)
lv_1 <- seq(1e-2, 6e-1, length.out = 15)
```

```{r s1-data}
set.seed(7)
search_data_1 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = FALSE,
                                   case          = 2,
                                   group_corr    = 0.7,
                                  scale = 0.15)
group_labels_1 <- search_data_1$group_labels
rank_check(search_data_1$Beta_matrix)
```

```{r}
plot_B_true_boxplot(search_data_1, group_labels = group_labels_1,title = "S1 & S2: True B — 10 groups, 40% zero")
```

```{r s1-fit}
set.seed(7)
sim_data1 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = FALSE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_1,
                              scale = 0.15)

auto_grplasso_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1,
  group_labels = group_labels_1, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5, rho = 0.1)

auto_lasso_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_ridge_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_mrcox_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)
```

```{r s1-results}
print_rank_comparisons(
  list(auto_grplasso_1, auto_lasso_1, auto_ridge_1, auto_mrcox_1),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S1: n=80, 10g, sz=10, 40% zero"
)
```

```{r s1-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_1, "rrr_grplasso",
                      title = "S1 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_1,    "rrr_lasso",
                      title = "S1 Lasso"),
  lambda_plot_by_rank(auto_ridge_1,    "rrr_ridge",
                      title = "S1 Ridge"),
  lambda_plot_by_rank(auto_mrcox_1,    "rrr_ridge",
                      title = "S1 MrCox"),
  
  ncol = 4)
```

# ============================================================
# S2: n=300, 10 groups (size=10), 40% zero  [n > p]
# ============================================================
```{r s2-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 10
zero_blocks <- c(1, 3, 5, 7)
lv_2        <- seq(1e-2, 6e-1, length.out = 15)
lv_pen_2    <- seq(2e-3, 2e-2, length.out = 10)
lv_mrcox_2  <- seq(1e-2, 1e-1, length.out = 10)
```

```{r s2-data}
set.seed(7)
search_data_2 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = TRUE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_2 <- search_data_2$group_labels
rank_check(search_data_2$Beta_matrix)
```

```{r s2-fit}
set.seed(7)
sim_data2 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = TRUE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_2)

auto_grplasso_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2,
  group_labels = group_labels_2, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2,
  method = "rrr_lasso", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_ridge_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2,
  method = "rrr_ridge", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_pen_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_pen_2,
  method = "pen", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_mrcox_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_mrcox_2,
  method = "mrcox", rank_vector = c(1, 2, 3), n_folds_cv = 5)
```

```{r s2-results}
print_rank_comparisons(
  list(auto_grplasso_2, auto_lasso_2, auto_ridge_2, auto_pen_2, auto_mrcox_2),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S2: n=300, 10g, sz=10, 40% zero"
)
```

```{r s2-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_2, "rrr_grplasso",
                      title = "S2 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_2,    "rrr_lasso",
                      title = "S2 Lasso"),
  lambda_plot_by_rank(auto_ridge_2,    "rrr_ridge",
                      title = "S2 Ridge"),
  lambda_plot_by_rank(auto_pen_2,      "pen",
                      title = "S2 Pen"),
  lambda_plot_by_rank(auto_mrcox_4,    "mrcox",
                      title = "S4 MrCox"),
  ncol = 5)
```

# ============================================================
# S3: n=80, 10 groups (size=10), 60% zero  [n < p, more sparse]
# ============================================================
```{r s3-setup}
n <- 80; p <- 100; r_true <- 2; k <- 4
n_groups    <- 10
zero_blocks <- c(1, 2, 3, 4, 5, 6)
lv_3 <- seq(1e-2, 6e-1, length.out = 15)
```

```{r s3-data}
set.seed(7)
search_data_3 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = FALSE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_3 <- search_data_3$group_labels
rank_check(search_data_3$Beta_matrix)
```

```{r}
plot_B_true_boxplot(search_data_3, group_labels = group_labels_2,title = "S3 & S4: True B — 10 groups, 60% zero")
```


```{r s3-fit}
set.seed(7)
sim_data3 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = FALSE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_3)

auto_grplasso_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3,
  group_labels = group_labels_3, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5, rho = 0.1)

auto_lasso_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_ridge_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_mrcox_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)
```

```{r s3-results}
print_rank_comparisons(
  list(auto_grplasso_3, auto_lasso_3, auto_ridge_3, auto_mrcox_3),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S3: n=80, 10g, sz=10, 60% zero"
)
```

```{r s3-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_3, "rrr_grplasso",
                      title = "S3 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_3,    "rrr_lasso",
                      title = "S3 Lasso"),
  lambda_plot_by_rank(auto_ridge_3,    "rrr_ridge",
                      title = "S3 Ridge"),
  lambda_plot_by_rank(auto_mrcox_3,    "mrcox",
                      title = "S3 MrCox"),
  ncol = 4)
```

# ============================================================
# S4: n=300, 10 groups (size=10), 60% zero  [n > p, more sparse]
# ============================================================
```{r s4-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 10
zero_blocks <- c(1, 2, 3, 4, 5, 6)
lv_4        <- seq(1e-2, 6e-1, length.out = 15)
lv_pen_4    <- seq(2e-3, 2e-2, length.out = 10)
lv_mrcox_4  <- seq(2e-2, 2e-1, length.out = 10)
```

```{r s4-data}
set.seed(7)
search_data_4 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = TRUE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_4 <- search_data_4$group_labels
rank_check(search_data_4$Beta_matrix)
```

```{r s4-fit}
set.seed(7)
sim_data4 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = TRUE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_4)

auto_grplasso_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4,
  group_labels = group_labels_4, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4,
  method = "rrr_lasso", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_ridge_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4,
  method = "rrr_ridge", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_pen_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_pen_4,
  method = "pen", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_mrcox_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_mrcox_4,
  method = "mrcox", rank_vector = c(1, 2, 3), n_folds_cv = 5)
```

```{r s4-results}
print_rank_comparisons(
  list(auto_grplasso_4, auto_lasso_4, auto_ridge_4, auto_pen_4, auto_mrcox_4),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S4: n=300, 10g, sz=10, 60% zero"
)
```

```{r s4-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_4, "rrr_grplasso",
                      title = "S4 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_4,    "rrr_lasso",
                      title = "S4 Lasso"),
  lambda_plot_by_rank(auto_ridge_4,    "rrr_ridge",
                      title = "S4 Ridge"),
  lambda_plot_by_rank(auto_pen_4,      "pen",
                      title = "S4 Pen"),
  lambda_plot_by_rank(auto_mrcox_4,    "mrcox",
                      title = "S4 MrCox"),
  ncol = 5)
```

# ============================================================
# S5: n=80, 20 groups (size=5), 40% zero  [n < p, more groups]
# ============================================================
```{r s5-setup}
n <- 80; p <- 100; r_true <- 2; k <- 4
n_groups    <- 20
zero_blocks <- c(1, 2, 3, 4, 5, 6, 7, 8)   # 8 of 20 groups → 40% zero
lv_5 <- seq(1e-2, 6e-1, length.out = 15)
```

```{r s5-data}
set.seed(7)
search_data_5 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = FALSE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_5 <- search_data_5$group_labels
rank_check(search_data_5$Beta_matrix)
```

```{r}
plot_B_true_boxplot(search_data_5, group_labels = group_labels_5,title = "S5 & S6: True B — 20 groups, 40% zero")
```

```{r s5-fit}
set.seed(7)
sim_data5 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = FALSE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_5)

auto_grplasso_5 <- simulations_fit_auto_rank(
  sim_data5, datas_cv = search_data_5, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_5,
  group_labels = group_labels_5, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5, rho = 0.1)

auto_lasso_5 <- simulations_fit_auto_rank(
  sim_data5, datas_cv = search_data_5, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_5,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_ridge_5 <- simulations_fit_auto_rank(
  sim_data5, datas_cv = search_data_5, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_5,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_mrcox_5 <- simulations_fit_auto_rank(
  sim_data5, datas_cv = search_data_5, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_5,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)
```

```{r s5-results}
print_rank_comparisons(
  list(auto_grplasso_5, auto_lasso_5, auto_ridge_5, auto_mrcox_5),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S5: n=80, 20g, sz=5, 40% zero"
)
```

```{r s5-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_5, "rrr_grplasso",
                      title = "S5 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_5,    "rrr_lasso",
                      title = "S5 Lasso"),
  lambda_plot_by_rank(auto_ridge_5,    "rrr_ridge",
                      title = "S5 Ridge"),
  lambda_plot_by_rank(auto_mrcox_5,    "mrcox",
                      title = "S5 MrCox"),
  ncol = 4)
```

# ============================================================
# S6: n=300, 20 groups (size=5), 40% zero  [n > p, more groups]
# ============================================================
```{r s6-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 20
zero_blocks <- c(1, 2, 3, 4, 5, 6, 7, 8)
lv_6        <- seq(1e-2, 6e-1, length.out = 15)
lv_pen_6    <- seq(2e-3, 2e-2, length.out = 10)
lv_mrcox_6  <- seq(1e-2, 1e-1, length.out = 10)
```

```{r s6-data}
set.seed(7)
search_data_6 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = TRUE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_6 <- search_data_6$group_labels
rank_check(search_data_6$Beta_matrix)
```

```{r s6-fit}
set.seed(7)
sim_data6 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = TRUE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_6)

auto_grplasso_6 <- simulations_fit_auto_rank(
  sim_data6, datas_cv = search_data_6, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_6,
  group_labels = group_labels_6, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_6 <- simulations_fit_auto_rank(
  sim_data6, datas_cv = search_data_6, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_6,
  method = "rrr_lasso", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_ridge_6 <- simulations_fit_auto_rank(
  sim_data6, datas_cv = search_data_6, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_6,
  method = "rrr_ridge", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_pen_6 <- simulations_fit_auto_rank(
  sim_data6, datas_cv = search_data_6, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_pen_6,
  method = "pen", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_mrcox_6 <- simulations_fit_auto_rank(
  sim_data6, datas_cv = search_data_6, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_mrcox_6,
  method = "mrcox", rank_vector = c(1, 2, 3), n_folds_cv = 5)
```

```{r s6-results}
print_rank_comparisons(
  list(auto_grplasso_6, auto_lasso_6, auto_ridge_6, auto_pen_6, auto_mrcox_6),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S6: n=300, 20g, sz=5, 40% zero"
)
```

```{r s6-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_6, "rrr_grplasso",
                      title = "S6 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_6,    "rrr_lasso",
                      title = "S6 Lasso"),
  lambda_plot_by_rank(auto_ridge_6,    "rrr_ridge",
                      title = "S6 Ridge"),
  lambda_plot_by_rank(auto_pen_6,      "pen",
                      title = "S6 Pen"),
  lambda_plot_by_rank(auto_mrcox_6,    "mrcox",
                      title = "S6 MrCox"),
  ncol = 5)
```

# ============================================================
# S7: n=80, 20 groups (size=5), 60% zero  [n < p, most sparse]
# ============================================================
```{r s7-setup}
n <- 80; p <- 100; r_true <- 2; k <- 4
n_groups    <- 20
zero_blocks <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)  # 12/20 → 60%
lv_7 <- seq(1e-2, 6e-1, length.out = 15)
```

```{r s7-data}
set.seed(7)
search_data_7 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = FALSE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_7 <- search_data_7$group_labels
rank_check(search_data_7$Beta_matrix)
```

```{r}
plot_B_true_boxplot(search_data_7, group_labels = group_labels_7,title = "S7 & S8: True B — 20 groups, 60% zero")
```

```{r s7-fit}
set.seed(7)
sim_data7 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = FALSE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_7)

auto_grplasso_7 <- simulations_fit_auto_rank(
  sim_data7, datas_cv = search_data_7, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_7,
  group_labels = group_labels_7, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5, rho = 0.1)

auto_lasso_7 <- simulations_fit_auto_rank(
  sim_data7, datas_cv = search_data_7, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_7,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_ridge_7 <- simulations_fit_auto_rank(
  sim_data7, datas_cv = search_data_7, p = p, k = k,
  n_simulations = 100, lambda_vector = seq(1e-2, 8e-1, length.out = 15),
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)

auto_mrcox_7 <- simulations_fit_auto_rank(
  sim_data7, datas_cv = search_data_7, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_7,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5, rho = 0.1)
```

```{r s7-results}
print_rank_comparisons(
  list(auto_grplasso_7, auto_lasso_7, auto_ridge_7, auto_mrcox_7),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S7: n=80, 20g, sz=5, 60% zero"
)
```

```{r s7-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_7, "rrr_grplasso",
                      title = "S7 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_7,    "rrr_lasso",
                      title = "S7 Lasso"),
  lambda_plot_by_rank(auto_ridge_7,    "rrr_ridge",
                      title = "S7 Ridge"),
  lambda_plot_by_rank(auto_mrcox_7,    "mrcox",
                      title = "S7 MrCox"),
  ncol = 3)
```

# ============================================================
# S8: n=300, 20 groups (size=5), 60% zero  [n > p, most sparse]
# ============================================================
```{r s8-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 20
zero_blocks <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 12)
lv_8        <- seq(1e-2, 6e-1, length.out = 15)
lv_pen_8    <- seq(2e-3, 2e-2, length.out = 10)
lv_mrcox_8  <- seq(1e-2, 1e-1, length.out = 10)
```

```{r s8-data}
set.seed(7)
search_data_8 <- simulations_data(n, p, r_true, k,
                                   n_simulations = 10,
                                   n_groups      = n_groups,
                                   zero_blocks   = zero_blocks,
                                   store_dlong   = TRUE,
                                   case          = 2,
                                   group_corr    = 0.7)
group_labels_8 <- search_data_8$group_labels
rank_check(search_data_8$Beta_matrix)
```

```{r s8-fit}
set.seed(7)
sim_data8 <- simulations_data(n, p, r_true, k,
                               n_simulations = 100,
                               n_groups      = n_groups,
                               zero_blocks   = zero_blocks,
                               store_dlong   = TRUE,
                               case          = 2,
                               group_corr    = 0.7,
                               beta_obj      = search_data_8)

auto_grplasso_8 <- simulations_fit_auto_rank(
  sim_data8, datas_cv = search_data_8, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_8,
  group_labels = group_labels_8, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_8 <- simulations_fit_auto_rank(
  sim_data8, datas_cv = search_data_8, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_8,
  method = "rrr_lasso", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_ridge_8 <- simulations_fit_auto_rank(
  sim_data8, datas_cv = search_data_8, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_8,
  method = "rrr_ridge", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_pen_8 <- simulations_fit_auto_rank(
  sim_data8, datas_cv = search_data_8, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_pen_8,
  method = "pen", rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_mrcox_8 <- simulations_fit_auto_rank(
  sim_data8, datas_cv = search_data_8, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_mrcox_8,
  method = "mrcox", rank_vector = c(1, 2, 3), n_folds_cv = 5)
```

```{r s8-results}
print_rank_comparisons(
  list(auto_grplasso_8, auto_lasso_8, auto_ridge_8, auto_pen_8, auto_mrcox_8),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S8: n=300, 20g, sz=5, 60% zero"
)
```

```{r s8-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_8, "rrr_grplasso",
                      title = "S8 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_8,    "rrr_lasso",
                      title = "S8 Lasso"),
  lambda_plot_by_rank(auto_ridge_8,    "rrr_ridge",
                      title = "S8 Ridge"),
  lambda_plot_by_rank(auto_pen_8,      "pen",
                      title = "S8 Pen"),
  lambda_plot_by_rank(auto_mrcox_8,    "mrcox",
                      title = "S8 MrCox"),
  ncol = 5)
```

# ============================================================
# Summary — best-rank results across all scenarios
# ============================================================
```{r summary-build}
# Helper: extract best-rank row, inserting NA for missing methods
add_missing_methods <- function(comp, all_methods) {
  for (m in all_methods) {
    if (!m %in% comp$method)
      comp <- rbind(comp,
                    data.frame(method = m, best_rank = NA,
                               mean_bias = NA, mean_mse = NA,
                               mean_corr = NA))
  }
  comp
}

all_methods <- c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox")

# Helper: wrap comparison_best_rank and fill in any missing methods
best_comp <- function(...) {
  fits    <- list(...)
  methods <- sapply(fits, function(x) x$all_results[[1]]$performance$method[1],
                    USE.NAMES = FALSE)
  # fallback: pass method names explicitly via a named list
  add_missing_methods(
    comparison_best_rank(fits, names(list(...))),
    all_methods)
}

# Build scenario table
# (fix: best_rank must stay integer → convert AFTER rbind)
make_row <- function(scenario_label, n_val, n_groups_val, zero_pct_val,
                     auto_grp, auto_las, auto_rid = NULL,
                     auto_pen = NULL, auto_mrc) {
  fits    <- Filter(Negate(is.null),
                    list(auto_grp, auto_las, auto_rid, auto_pen, auto_mrc))
  mnames  <- Filter(Negate(is.null),
                    list(
                      if (!is.null(auto_grp)) "rrr_grplasso",
                      if (!is.null(auto_las)) "rrr_lasso",
                      if (!is.null(auto_rid)) "rrr_ridge",
                      if (!is.null(auto_pen)) "pen",
                      if (!is.null(auto_mrc)) "mrcox"))
  comp    <- comparison_best_rank(fits, unlist(mnames))
  comp    <- add_missing_methods(comp, all_methods)
  cbind(scenario   = scenario_label,
        n          = n_val,
        n_groups   = n_groups_val,
        zero_pct   = zero_pct_val,
        comp,
        stringsAsFactors = FALSE)
}

all_comparison <- rbind(
  make_row("S1: n=80,  10g, sz=10, 40%",  80,  10, "40%",
           auto_grplasso_1, auto_lasso_1, auto_ridge_1,         NULL,       auto_mrcox_1),
  make_row("S2: n=300, 10g, sz=10, 40%", 300,  10, "40%",
           auto_grplasso_2, auto_lasso_2, auto_ridge_2, auto_pen_2, auto_mrcox_2),
  make_row("S3: n=80,  10g, sz=10, 60%",  80,  10, "60%",
           auto_grplasso_3, auto_lasso_3, auto_ridge_3,         NULL,       auto_mrcox_3),
  make_row("S4: n=300, 10g, sz=10, 60%", 300,  10, "60%",
           auto_grplasso_4, auto_lasso_4, auto_ridge_4, auto_pen_4, auto_mrcox_4),
  make_row("S5: n=80,  20g, sz=5,  40%",  80,  20, "40%",
           auto_grplasso_5, auto_lasso_5, auto_ridge_5,         NULL,       auto_mrcox_5),
  make_row("S6: n=300, 20g, sz=5,  40%", 300,  20, "40%",
           auto_grplasso_6, auto_lasso_6, auto_ridge_6, auto_pen_6, auto_mrcox_6),
  make_row("S7: n=80,  20g, sz=5,  60%",  80,  20, "60%",
           auto_grplasso_7, auto_lasso_7, auto_ridge_7,         NULL,       auto_mrcox_7),
  make_row("S8: n=300, 20g, sz=5,  60%", 300,  20, "60%",
           auto_grplasso_8, auto_lasso_8, auto_ridge_8, auto_pen_8, auto_mrcox_8)
) %>%
  mutate(
    across(c(n, n_groups, mean_mse, mean_bias, mean_corr), as.numeric),
    best_rank    = as.integer(best_rank),           # ← keep as integer
    method_label = dplyr::case_when(
      method == "rrr_grplasso" ~ "Group Lasso",
      method == "rrr_lasso"   ~ "Lasso",
      method == "rrr_ridge"   ~ "Ridge",
      method == "pen"         ~ "Pen",
      method == "mrcox"       ~ "MrCox",
      TRUE                    ~ method),
    method_label = factor(method_label,
                          levels = c("Group Lasso", "Lasso",
                                     "Ridge", "Pen", "MrCox"))
  )
rownames(all_comparison) <- NULL
```

```{r summary-table}
all_comparison %>%
  select(scenario, method_label, best_rank, mean_mse, mean_bias, mean_corr) %>%
  arrange(scenario, method_label) %>%
  mutate(across(c(mean_mse, mean_bias, mean_corr), ~ round(.x, 4))) %>%
  print(n = Inf)
```

```{r summary-barplot, fig.width=11, fig.height=5}
colors5 <- c("Group Lasso" = "steelblue", "Lasso"  = "tomato",
             "Ridge"       = "darkorange", "Pen"   = "darkgreen",
             "MrCox"       = "purple")

scenario_order <- all_comparison %>%
  filter(method == "rrr_grplasso") %>%
  arrange(desc(mean_mse)) %>%
  pull(scenario)

all_comparison <- all_comparison %>%
  mutate(scenario = factor(scenario, levels = scenario_order))

p_mse <- ggplot(all_comparison,
                aes(x = scenario, y = mean_mse, fill = method_label)) +
  geom_bar(stat = "identity",
           position = position_dodge(width = 0.8),
           alpha = 0.88, width = 0.75, na.rm = TRUE) +
  scale_fill_manual(values = colors5, name = "Method") +
  scale_y_continuous(labels = number_format(accuracy = 0.001)) +
  labs(title    = "Mean MSE by scenario and method (at auto-selected rank)",
       subtitle = "p=100, k=4, group_corr=0.7, fixed Beta\n(Pen/Ridge: n=300 only; Ridge: new addition)",
       x = NULL, y = "Mean MSE") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x        = element_text(angle = 35, hjust = 1, size = 9),
        legend.position    = "bottom",
        panel.grid.major.x = element_blank())
print(p_mse)
```

```{r summary-lineplot, fig.width=11, fig.height=7}
p_line <- all_comparison %>%
  mutate(
    group_size  = 100 / n_groups,
    facet_label = paste0(n_groups, " groups (sz=", group_size, "), ",
                         zero_pct, " zero"),
    facet_label = factor(facet_label,
                         levels = c("10 groups (sz=10), 40% zero",
                                    "10 groups (sz=10), 60% zero",
                                    "20 groups (sz=5), 40% zero",
                                    "20 groups (sz=5), 60% zero"))
  ) %>%
  ggplot(aes(x = factor(n), y = mean_mse,
             color = method_label, group = method_label,
             shape = method_label)) +
  geom_line(linewidth = 0.9, na.rm = TRUE) +
  geom_point(size = 3, na.rm = TRUE) +
  facet_wrap(~facet_label, nrow = 2, scales = "free_y") +
  scale_color_manual(values = colors5, name = "Method") +
  scale_shape_manual(values = c("Group Lasso" = 16, "Lasso" = 17,
                                 "Ridge" = 15, "Pen" = 8, "MrCox" = 18),
                     name = "Method") +
  labs(title    = "Mean MSE by sample size (at auto-selected rank)",
       subtitle = "p=100, k=4, group_corr=0.7  |  Pen & Ridge: n=300 only",
       x = "Sample size (n)", y = "Mean MSE") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        strip.text      = element_text(size = 10, face = "bold"),
        panel.spacing   = unit(1.2, "lines"))
print(p_line)
```

```{r summary-corrplot, fig.width=11, fig.height=5}
# Mean correlation (higher = better)
p_corr <- ggplot(all_comparison,
                 aes(x = scenario, y = mean_corr, fill = method_label)) +
  geom_bar(stat = "identity",
           position = position_dodge(width = 0.8),
           alpha = 0.88, width = 0.75, na.rm = TRUE) +
  scale_fill_manual(values = colors5, name = "Method") +
  scale_y_continuous(limits = c(0, 1),
                     labels = number_format(accuracy = 0.01)) +
  labs(title = "Mean correlation(B_hat, B_true) by scenario and method",
       x = NULL, y = "Mean correlation") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x        = element_text(angle = 35, hjust = 1, size = 9),
        legend.position    = "bottom",
        panel.grid.major.x = element_blank())
print(p_corr)
```

# ============================================================
# Beta heatmaps — Group Lasso best-rank estimates vs truth
# ============================================================
```{r heatmaps, fig.width=9, fig.height=4}
minb <- 0; maxb <- 2

compare_beta_heatmap("S1: n=80,  10g, 40%", sim_data1, auto_grplasso_1$best_perf, minb, maxb)
compare_beta_heatmap("S2: n=300, 10g, 40%", sim_data2, auto_grplasso_2$best_perf, minb, maxb)

```

