---
title: "simulation_estimated_Beta"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Source packages and files
```{r}
library(Rcpp)
library(RcppEigen)
library(mstate)
library(tidyr)
library(tidyverse)
library(dplyr)
library(ggplot2)
library(scales)
library(patchwork)

sourceCpp("group_lasso_gd/grplasso_survrrr.cpp")
source("group_lasso_gd/grplasso_survrrr.R")
sourceCpp("lasso_gd/lasso_survrrr.cpp")
source("lasso_gd/lasso_survrrr.R")
sourceCpp("ridge_gd/ridge_survrrr.cpp")
source("ridge_gd/ridge_survrrr.R")
sourceCpp("mrcox/aligned.cpp")
source("mrcox/mrcox.R")
source("lasso_cc/survRRR_functions.R")
source("simdata_function_and_performance_functions.R")
```


# Global parameters for case = 2
```{r global-case2-params}
rho_w <- 0.7    # within-group correlation for KMS Toeplitz on alpha
rho_b <- 0.1    # between-group correlation for KMS Toeplitz on alpha
rho_w_k <- 0.7    # within-group correlation for KMS Toeplitz on Gamma
rho_b_k <- 0.1    # between-group correlation for KMS Toeplitz on Gamma
mu_l <- 0.2    # lower bound for group mean (active groups)
mu_u  <- 1.0   # upper bound for group mean (active groups)
use_kms_beta <- TRUE  # use KMS covariance for A_matrix columns
```

# ============================================================
# S0: Low-dimensional, no penalization
# p=20, n=300, case=1
# ============================================================
```{r s0-data}
n <- 300; p <- 20; r_true <- 2; k <- 4

set.seed(7)
sim_data0 <- simulations_data(n, p, r_true, k,
                              case = 1,
                              n_simulations = 100,
                              target_sd = 1,
                              target_event_rate = 0.6,
                              store_dlong = TRUE)

generate_data_plots(sim_data0$dlong_list[[1]], n = n, r = r_true, p = p, k = k)
```

```{r s0-fit}
# lambda = 0
lv_0 <- 0

set.seed(7)
auto_grplasso_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, group_labels = rep(1L, p),
  method = "rrr_grplasso", rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_lasso_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "rrr_lasso",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_ridge_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "rrr_ridge",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_pen_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "pen",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)

auto_mrcox_0 <- simulations_fit_auto_rank(
  sim_data0, p = p, k = k, n_simulations = 100,
  lambda_vector = lv_0, method = "mrcox",
  rank_vector = c(1, 2, 3), n_datasets_cv = 10)
```

```{r s0-results}
print_rank_comparisons(
  list(auto_grplasso_0, auto_lasso_0, auto_ridge_0, auto_pen_0, auto_mrcox_0),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S0: n=300, p=20, case=1, lambda=0"
)
```

# ============================================================
# Penalized scenarios — case=2
# Four scenarios at fixed n=300, k=4, r_true=2, 40% zero groups.
# pen is omitted in n < p settings
# ============================================================

# ============================================================
# S1: n=300, p=600, 10 groups, 40% zero  [n < p]
# ============================================================
```{r s1-setup}
n <- 300; p <- 600; r_true <- 2; k <- 4
n_groups    <- 10
n_groups_k  <- 2
zero_blocks <- c(1, 3, 5, 7)                                # 4 / 10 = 40% zero
lv_1          <- seq(1e-2, 2.5e-1, length.out = 11)
lv_1_ridge    <- seq(5e-1, 1.5,  length.out = 11)
lv_1_grplasso <- seq(1e-1, 1, length.out = 11)
lv_1_mrcox    <- seq(1e-2, 2e-1, length.out = 11)
```

```{r s1-data}
set.seed(6)
search_data_1 <- simulations_data(n, p, r_true, k,
                                  n_simulations = 10,
                                  case = 2,
                                  target_sd = 1,
                                  target_event_rate = 0.6,
                                  n_groups   = n_groups,
                                  n_groups_k = n_groups_k,
                                  zero_blocks = zero_blocks,
                                  store_dlong = FALSE,
                                  n_probe = 300)
group_labels_1 <- search_data_1$group_labels
rank_check(search_data_1$Beta_matrix)
```

```{r s1-Btrue, fig.width=8, fig.height=4}
plot_B_true_boxplot(search_data_1, group_labels = group_labels_1,
                    title = "S1: True B — n=300, p=600, 10 groups, 40% zero")
```

```{r s1-fit}
set.seed(6)
sim_data1 <- simulations_data(n, p, r_true, k,
                              n_simulations = 100,
                              case = 2,
                              target_sd = 1,
                              target_event_rate = 0.6,
                              n_groups   = n_groups,
                              n_groups_k = n_groups_k,
                              zero_blocks = zero_blocks,
                              store_dlong = FALSE,
                              n_probe = 300,
                              beta_obj = search_data_1)

auto_grplasso_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1_grplasso,
  group_labels = group_labels_1, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_ridge_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1_ridge,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_mrcox_1 <- simulations_fit_auto_rank(
  sim_data1, datas_cv = search_data_1, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_1_mrcox,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)
```

```{r s1-results}
print_rank_comparisons(
  list(auto_grplasso_1, auto_lasso_1, auto_ridge_1, auto_mrcox_1),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S1: n=300, p=600, 10groups, 40% zero"
)
```

```{r s1-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_1, "rrr_grplasso", title = "S1 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_1,    "rrr_lasso",    title = "S1 Lasso"),
  lambda_plot_by_rank(auto_ridge_1,    "rrr_ridge",    title = "S1 Ridge"),
  lambda_plot_by_rank(auto_mrcox_1,    "mrcox",        title = "S1 MrCox"),
  ncol = 4
)
```

## S1 — plot_B_mean_vs_true
```{r s1-mvt-grp}
plot_B_mean_vs_true(auto_grplasso_1, sim_data1)
```
```{r s1-mvt-las}
plot_B_mean_vs_true(auto_lasso_1, sim_data1)
```
```{r s1-mvt-rid}
plot_B_mean_vs_true(auto_ridge_1, sim_data1)
```
```{r s1-mvt-mrc}
plot_B_mean_vs_true(auto_mrcox_1, sim_data1)
```

## S1 — plot_B_recovery_boxplot
```{r s1-box-grp}
plot_B_recovery_boxplot(auto_grplasso_1, sim_data1, group_labels = group_labels_1)
```
```{r s1-box-las}
plot_B_recovery_boxplot(auto_lasso_1, sim_data1)
```
```{r s1-box-rid}
plot_B_recovery_boxplot(auto_ridge_1, sim_data1)
```
```{r s1-box-mrc}
plot_B_recovery_boxplot(auto_mrcox_1, sim_data1)
```

## S1 — plot_group_activity
```{r s1-act-grp}
plot_group_activity(auto_grplasso_1, sim_data1, group_labels = group_labels_1)
```
```{r s1-act-las}
plot_group_activity(auto_lasso_1, sim_data1)
```
```{r s1-act-rid}
plot_group_activity(auto_ridge_1, sim_data1)
```
```{r s1-act-mrc}
plot_group_activity(auto_mrcox_1, sim_data1)
```

# ============================================================
# S2: n=300, p=600, 25 groups, 40% zero  [n < p]
# ============================================================
```{r s2-setup}
n <- 300; p <- 600; r_true <- 2; k <- 4
n_groups    <- 25
n_groups_k  <- 2
zero_blocks <- c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19)         # 10 / 25 = 40% zero
lv_2          <- seq(1e-2, 2.5e-1, length.out = 11)
lv_2_ridge    <- seq(8e-1, 2,  length.out = 11)
lv_2_grplasso <- seq(1e-1, 1, length.out = 11)
lv_2_mrcox    <- seq(1e-2, 2e-1, length.out = 11)
```

```{r s2-data}
set.seed(6)
search_data_2 <- simulations_data(n, p, r_true, k,
                                  n_simulations = 10,
                                  case = 2,
                                  target_sd = 1,
                                  target_event_rate = 0.6,
                                  n_groups   = n_groups,
                                  n_groups_k = n_groups_k,
                                  zero_blocks = zero_blocks,
                                  store_dlong = FALSE,
                                  n_probe = 300)
group_labels_2 <- search_data_2$group_labels
rank_check(search_data_2$Beta_matrix)
```

```{r s2-Btrue, fig.width=8, fig.height=4}
plot_B_true_boxplot(search_data_2, group_labels = group_labels_2,
                    title = "S2: True B — n=300, p=600, 25groups, 40% zero")
```

```{r s2-fit}
set.seed(6)
sim_data2 <- simulations_data(n, p, r_true, k,
                              n_simulations = 100,
                              case = 2,
                              target_sd = 1,
                              target_event_rate = 0.6,
                              n_groups   = n_groups,
                              n_groups_k = n_groups_k,
                              zero_blocks = zero_blocks,
                              store_dlong = FALSE,
                              n_probe = 300,
                              beta_obj = search_data_2)

auto_grplasso_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2_grplasso,
  group_labels = group_labels_2, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_ridge_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2_ridge,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_mrcox_2 <- simulations_fit_auto_rank(
  sim_data2, datas_cv = search_data_2, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_2_mrcox,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)
```

```{r s2-results}
print_rank_comparisons(
  list(auto_grplasso_2, auto_lasso_2, auto_ridge_2, auto_mrcox_2),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "mrcox"),
  "S2: n=300, p=600, 25groups, 40% zero"
)
```

```{r s2-lambda-plots, fig.width=10, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_2, "rrr_grplasso", title = "S2 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_2,    "rrr_lasso",    title = "S2 Lasso"),
  lambda_plot_by_rank(auto_ridge_2,    "rrr_ridge",    title = "S2 Ridge"),
  lambda_plot_by_rank(auto_mrcox_2,    "mrcox",        title = "S2 MrCox"),
  ncol = 4
)
```

## S2 — plot_B_mean_vs_true
```{r s2-mvt-grp}
plot_B_mean_vs_true(auto_grplasso_2, sim_data2)
```
```{r s2-mvt-las}
plot_B_mean_vs_true(auto_lasso_2, sim_data2)
```
```{r s2-mvt-rid}
plot_B_mean_vs_true(auto_ridge_2, sim_data2)
```
```{r s2-mvt-mrc}
plot_B_mean_vs_true(auto_mrcox_2, sim_data2)
```

## S2 — plot_B_recovery_boxplot
```{r s2-box-grp}
plot_B_recovery_boxplot(auto_grplasso_2, sim_data2, group_labels = group_labels_2)
```
```{r s2-box-las}
plot_B_recovery_boxplot(auto_lasso_2, sim_data2)
```
```{r s2-box-rid}
plot_B_recovery_boxplot(auto_ridge_2, sim_data2)
```
```{r s2-box-mrc}
plot_B_recovery_boxplot(auto_mrcox_2, sim_data2)
```

## S2 — plot_group_activity
```{r s2-act-grp}
plot_group_activity(auto_grplasso_2, sim_data2, group_labels = group_labels_2)
```
```{r s2-act-las}
plot_group_activity(auto_lasso_2, sim_data2)
```
```{r s2-act-rid}
plot_group_activity(auto_ridge_2, sim_data2)
```
```{r s2-act-mrc}
plot_group_activity(auto_mrcox_2, sim_data2)
```

# ============================================================
# S3: n=300, p=100, 10 groups (sz=10), 40% zero  [n > p]
# pen included
# ============================================================
```{r s3-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 10
n_groups_k  <- 2
zero_blocks <- c(1, 3, 5, 7)                                # 4 / 10 = 40% zero
lv_3          <- seq(1e-2, 2.5e-1, length.out = 11)
lv_3_ridge    <- seq(2e-1, 1.2,  length.out = 11)
lv_3_grplasso <- seq(5e-2, 5e-1, length.out = 11)
lv_3_mrcox    <- seq(1e-2, 2e-1, length.out = 11)
lv_3_pen      <- seq(2e-3, 3e-2, length.out = 11)
```

```{r s3-data}
set.seed(7)
search_data_3 <- simulations_data(n, p, r_true, k,
                                  n_simulations = 10,
                                  case = 2,
                                  target_sd = 1,
                                  target_event_rate = 0.6,
                                  n_groups   = n_groups,
                                  n_groups_k = n_groups_k,
                                  zero_blocks = zero_blocks,
                                  store_dlong = TRUE,
                                  n_probe = 300)
group_labels_3 <- search_data_3$group_labels
rank_check(search_data_3$Beta_matrix)
```

```{r s3-Btrue, fig.width=8, fig.height=4}
plot_B_true_boxplot(search_data_3, group_labels = group_labels_3,
                    title = "S3: True B — n=300, p=100, 10g (sz=10), 40% zero")
```

```{r s3-fit}
set.seed(7)
sim_data3 <- simulations_data(n, p, r_true, k,
                              n_simulations = 100,
                              case = 2,
                              target_sd = 1,
                              target_event_rate = 0.6,
                              n_groups   = n_groups,
                              n_groups_k = n_groups_k,
                              zero_blocks = zero_blocks,
                              store_dlong = TRUE,
                              n_probe = 300,
                              beta_obj = search_data_3)

auto_grplasso_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3_grplasso,
  group_labels = group_labels_3, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_ridge_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3_ridge,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_pen_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3_pen,
  method = "pen", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_mrcox_3 <- simulations_fit_auto_rank(
  sim_data3, datas_cv = search_data_3, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_3_mrcox,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)
```

```{r s3-results}
print_rank_comparisons(
  list(auto_grplasso_3, auto_lasso_3, auto_ridge_3, auto_pen_3, auto_mrcox_3),
  c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox"),
  "S3: n=300, p=100, 10g (sz=10), 40% zero"
)
```

```{r s3-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_3, "rrr_grplasso", title = "S3 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_3,    "rrr_lasso",    title = "S3 Lasso"),
  lambda_plot_by_rank(auto_ridge_3,    "rrr_ridge",    title = "S3 Ridge"),
  lambda_plot_by_rank(auto_pen_3,      "pen",          title = "S3 Pen"),
  lambda_plot_by_rank(auto_mrcox_3,    "mrcox",        title = "S3 MrCox"),
  ncol = 5
)
```

## S3 — plot_B_mean_vs_true
```{r s3-mvt-grp}
plot_B_mean_vs_true(auto_grplasso_3, sim_data3)
```
```{r s3-mvt-las}
plot_B_mean_vs_true(auto_lasso_3, sim_data3)
```
```{r s3-mvt-rid}
plot_B_mean_vs_true(auto_ridge_3, sim_data3)
```
```{r s3-mvt-pen}
plot_B_mean_vs_true(auto_pen_3, sim_data3)
```
```{r s3-mvt-mrc}
plot_B_mean_vs_true(auto_mrcox_3, sim_data3)
```

## S3 — plot_B_recovery_boxplot
```{r s3-box-grp}
plot_B_recovery_boxplot(auto_grplasso_3, sim_data3, group_labels = group_labels_3)
```
```{r s3-box-las}
plot_B_recovery_boxplot(auto_lasso_3, sim_data3)
```
```{r s3-box-rid}
plot_B_recovery_boxplot(auto_ridge_3, sim_data3)
```
```{r s3-box-pen}
plot_B_recovery_boxplot(auto_pen_3, sim_data3)
```
```{r s3-box-mrc}
plot_B_recovery_boxplot(auto_mrcox_3, sim_data3)
```

## S3 — plot_group_activity
```{r s3-act-grp}
plot_group_activity(auto_grplasso_3, sim_data3, group_labels = group_labels_3)
```
```{r s3-act-las}
plot_group_activity(auto_lasso_3, sim_data3)
```
```{r s3-act-rid}
plot_group_activity(auto_ridge_3, sim_data3)
```
```{r s3-act-pen}
plot_group_activity(auto_pen_3, sim_data3)
```
```{r s3-act-mrc}
plot_group_activity(auto_mrcox_3, sim_data3)
```

# ============================================================
# S4: n=300, p=100, 25 groups (sz=4), 40% zero  [n > p]
# pen included
# ============================================================
```{r s4-setup}
n <- 300; p <- 100; r_true <- 2; k <- 4
n_groups    <- 25
n_groups_k  <- 2
zero_blocks <- c(1, 3, 5, 7, 9, 11, 13, 15, 17, 19)         # 10 / 25 = 40% zero
lv_4          <- seq(1e-2, 2.5e-1, length.out = 11)
lv_4_ridge    <- seq(2e-1, 1.2,  length.out = 11)
lv_4_grplasso <- seq(5e-2, 4e-1, length.out = 11)
lv_4_mrcox    <- seq(1e-2, 2e-1, length.out = 11)
lv_4_pen      <- seq(2e-3, 3e-2, length.out = 11)
```

```{r s4-data}
set.seed(8)
search_data_4 <- simulations_data(n, p, r_true, k,
                                  n_simulations = 10,
                                  case = 2,
                                  target_sd = 1,
                                  target_event_rate = 0.6,
                                  n_groups   = n_groups,
                                  n_groups_k = n_groups_k,
                                  zero_blocks = zero_blocks,
                                  store_dlong = TRUE,
                                  n_probe = 300)
group_labels_4 <- search_data_4$group_labels
rank_check(search_data_4$Beta_matrix)
```

```{r s4-Btrue, fig.width=8, fig.height=4}
plot_B_true_boxplot(search_data_4, group_labels = group_labels_4,
                    title = "S4: True B — n=300, p=100, 25g (sz=4), 40% zero")
```

```{r s4-fit}
set.seed(7)
sim_data4 <- simulations_data(n, p, r_true, k,
                              n_simulations = 100,
                              case = 2,
                              target_sd = 1,
                              target_event_rate = 0.6,
                              n_groups   = n_groups,
                              n_groups_k = n_groups_k,
                              zero_blocks = zero_blocks,
                              store_dlong = TRUE,
                              n_probe = 300,
                              beta_obj = search_data_4)

auto_grplasso_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4_grplasso,
  group_labels = group_labels_4, method = "rrr_grplasso",
  rank_vector = c(1, 2, 3), n_folds_cv = 5)

auto_lasso_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4,
  method = "rrr_lasso", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_ridge_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4_ridge,
  method = "rrr_ridge", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_pen_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4_pen,
  method = "pen", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)

auto_mrcox_4 <- simulations_fit_auto_rank(
  sim_data4, datas_cv = search_data_4, p = p, k = k,
  n_simulations = 100, lambda_vector = lv_4_mrcox,
  method = "mrcox", rank_vector = c(1, 2, 3),
  n_folds_cv = 5)
```

```{r s4-lambda-plots, fig.width=13, fig.height=4}
gridExtra::grid.arrange(
  lambda_plot_by_rank(auto_grplasso_4, "rrr_grplasso", title = "S4 Group Lasso"),
  lambda_plot_by_rank(auto_lasso_4,    "rrr_lasso",    title = "S4 Lasso"),
  lambda_plot_by_rank(auto_ridge_4,    "rrr_ridge",    title = "S4 Ridge"),
  lambda_plot_by_rank(auto_pen_4,      "pen",          title = "S4 Pen"),
  lambda_plot_by_rank(auto_mrcox_4,    "mrcox",        title = "S4 MrCox"),
  ncol = 5
)
```

## S4 — plot_B_mean_vs_true
```{r s4-mvt-grp}
plot_B_mean_vs_true(auto_grplasso_4, sim_data4)
```
```{r s4-mvt-las}
plot_B_mean_vs_true(auto_lasso_4, sim_data4)
```
```{r s4-mvt-rid}
plot_B_mean_vs_true(auto_ridge_4, sim_data4)
```
```{r s4-mvt-pen}
plot_B_mean_vs_true(auto_pen_4, sim_data4)
```
```{r s4-mvt-mrc}
plot_B_mean_vs_true(auto_mrcox_4, sim_data4)
```

## S4 — plot_B_recovery_boxplot
```{r s4-box-grp}
plot_B_recovery_boxplot(auto_grplasso_4, sim_data4, group_labels = group_labels_4)
```
```{r s4-box-las}
plot_B_recovery_boxplot(auto_lasso_4, sim_data4)
```
```{r s4-box-rid}
plot_B_recovery_boxplot(auto_ridge_4, sim_data4)
```
```{r s4-box-pen}
plot_B_recovery_boxplot(auto_pen_4, sim_data4)
```
```{r s4-box-mrc}
plot_B_recovery_boxplot(auto_mrcox_4, sim_data4)
```

## S4 — plot_group_activity
```{r s4-act-grp}
plot_group_activity(auto_grplasso_4, sim_data4, group_labels = group_labels_4)
```
```{r s4-act-las}
plot_group_activity(auto_lasso_4, sim_data4)
```
```{r s4-act-rid}
plot_group_activity(auto_ridge_4, sim_data4)
```
```{r s4-act-pen}
plot_group_activity(auto_pen_4, sim_data4)
```
```{r s4-act-mrc}
plot_group_activity(auto_mrcox_4, sim_data4)
```

# ============================================================
# Summary — best-rank results across all scenarios
# ============================================================
```{r summary-build}
# extract best-rank row, inserting NA for missing methods
add_missing_methods <- function(comp, all_methods) {
  for (m in all_methods) {
    if (!m %in% comp$method)
      comp <- rbind(comp,
                    data.frame(method = m, best_rank = NA,
                               mean_bias = NA, mean_mse = NA,
                               mean_rel_bias = NA, mean_nmse = NA,
                               mean_corr = NA))
  }
  comp
}

all_methods <- c("rrr_grplasso", "rrr_lasso", "rrr_ridge", "pen", "mrcox")

# Build scenario table
# (fix: best_rank must stay integer → convert AFTER rbind)
# Now: 'p' replaces the old 'n' axis since n is constant at 300.
make_row <- function(scenario_label, p_val, n_groups_val, zero_pct_val,
                     auto_grp, auto_las, auto_rid = NULL,
                     auto_pen = NULL, auto_mrc) {
  fits    <- Filter(Negate(is.null),
                    list(auto_grp, auto_las, auto_rid, auto_pen, auto_mrc))
  mnames  <- Filter(Negate(is.null),
                    list(
                      if (!is.null(auto_grp)) "rrr_grplasso",
                      if (!is.null(auto_las)) "rrr_lasso",
                      if (!is.null(auto_rid)) "rrr_ridge",
                      if (!is.null(auto_pen)) "pen",
                      if (!is.null(auto_mrc)) "mrcox"))
  comp    <- comparison_best_rank(fits, unlist(mnames))
  comp    <- add_missing_methods(comp, all_methods)
  cbind(scenario   = scenario_label,
        p          = p_val,
        n_groups   = n_groups_val,
        zero_pct   = zero_pct_val,
        comp,
        stringsAsFactors = FALSE)
}

all_comparison <- rbind(
  make_row("S1: p=600, 10g, sz=60, 40%", 600, 10, "40%",
           auto_grplasso_1, auto_lasso_1, auto_ridge_1,        NULL,        auto_mrcox_1),
  make_row("S2: p=600, 25g, sz=24, 40%", 600, 25, "40%",
           auto_grplasso_2, auto_lasso_2, auto_ridge_2,        NULL,        auto_mrcox_2),
  make_row("S3: p=100, 10g, sz=10, 40%", 100, 10, "40%",
           auto_grplasso_3, auto_lasso_3, auto_ridge_3, auto_pen_3,  auto_mrcox_3),
  make_row("S4: p=100, 25g, sz=4,  40%", 100, 25, "40%",
           auto_grplasso_4, auto_lasso_4, auto_ridge_4, auto_pen_4,  auto_mrcox_4)
) %>%
  mutate(
    across(c(p, n_groups, mean_mse, mean_bias, mean_rel_bias, mean_nmse, mean_corr), as.numeric),
    best_rank    = as.integer(best_rank),           # ← keep as integer
    method_label = dplyr::case_when(
      method == "rrr_grplasso" ~ "Group Lasso",
      method == "rrr_lasso"   ~ "Lasso",
      method == "rrr_ridge"   ~ "Ridge",
      method == "pen"         ~ "Pen",
      method == "mrcox"       ~ "MrCox",
      TRUE                    ~ method),
    method_label = factor(method_label,
                          levels = c("Group Lasso", "Lasso",
                                     "Ridge", "Pen", "MrCox"))
  )
rownames(all_comparison) <- NULL
```

```{r summary-barplot, fig.width=11, fig.height=5}
colors5 <- c("Group Lasso" = "steelblue", "Lasso"  = "tomato",
             "Ridge"       = "darkorange", "Pen"   = "darkgreen",
             "MrCox"       = "purple")

scenario_order <- all_comparison %>%
  filter(method == "rrr_grplasso") %>%
  arrange(desc(mean_mse)) %>%
  pull(scenario)

all_comparison <- all_comparison %>%
  mutate(scenario = factor(scenario, levels = scenario_order))

p_mse <- ggplot(all_comparison,
                aes(x = scenario, y = mean_mse, fill = method_label)) +
  geom_bar(stat = "identity",
           position = position_dodge(width = 0.8),
           alpha = 0.88, width = 0.75, na.rm = TRUE) +
  scale_fill_manual(values = colors5, name = "Method") +
  scale_y_continuous(labels = number_format(accuracy = 0.001)) +
  labs(title    = "Mean MSE by scenario and method (at auto-selected rank)",
       subtitle = "n=300, k=4, r_true=2, 40% zero groups, fixed Beta\n(Pen included only for p=100; omitted for p=600)",
       x = NULL, y = "Mean MSE") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x        = element_text(angle = 35, hjust = 1, size = 9),
        legend.position    = "bottom",
        panel.grid.major.x = element_blank())
print(p_mse)
```

```{r summary-lineplot, fig.width=11, fig.height=6}
# n is constant at 300; we vary p instead.
# Facet by n_groups (10 vs 25), x = p (100 vs 600).
p_line <- all_comparison %>%
  mutate(
    facet_label = paste0(n_groups, " groups, ", zero_pct, " zero"),
    facet_label = factor(facet_label,
                         levels = c("10 groups, 40% zero",
                                    "25 groups, 40% zero"))
  ) %>%
  ggplot(aes(x = factor(p), y = mean_mse,
             color = method_label, group = method_label,
             shape = method_label)) +
  geom_line(linewidth = 0.9, na.rm = TRUE) +
  geom_point(size = 3, na.rm = TRUE) +
  facet_wrap(~facet_label, nrow = 1, scales = "free_y") +
  scale_color_manual(values = colors5, name = "Method") +
  scale_shape_manual(values = c("Group Lasso" = 16, "Lasso" = 17,
                                 "Ridge" = 15, "Pen" = 8, "MrCox" = 18),
                     name = "Method") +
  labs(title    = "Mean MSE by p (at auto-selected rank)",
       subtitle = "n=300, k=4, r_true=2  |  Pen included only for p=100",
       x = "Number of predictors (p)", y = "Mean MSE") +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        strip.text      = element_text(size = 10, face = "bold"),
        panel.spacing   = unit(1.2, "lines"))
print(p_line)
```

```{r summary-corrplot, fig.width=11, fig.height=5}
# Mean correlation (higher = better)
p_corr <- ggplot(all_comparison,
                 aes(x = scenario, y = mean_corr, fill = method_label)) +
  geom_bar(stat = "identity",
           position = position_dodge(width = 0.8),
           alpha = 0.88, width = 0.75, na.rm = TRUE) +
  scale_fill_manual(values = colors5, name = "Method") +
  scale_y_continuous(limits = c(0, 1),
                     labels = number_format(accuracy = 0.01)) +
  labs(title = "Mean correlation(B_hat, B_true) by scenario and method",
       x = NULL, y = "Mean correlation") +
  theme_minimal(base_size = 12) +
  theme(axis.text.x        = element_text(angle = 35, hjust = 1, size = 9),
        legend.position    = "bottom",
        panel.grid.major.x = element_blank())
print(p_corr)
```


